---
title: "p8105_hw3_zj2379"
author: "Zheshu Jiang"
date: "2023-10-12"
output: github_document
---

## Problem1
```{r}
library(p8105.datasets)
data("instacart")
library(tidyverse)
library(ggridges)
library(patchwork)
```

```{r}
instacart |> 
  count(aisle) |> 
  arrange(desc(n))
```

There are 134 aisles, with fresh vegetables and fresh fruits holding the most items ordered.

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
instacart |> 
  count(aisle) |> 
  filter(n > 10000) |> 
  mutate(aisle = fct_reorder(aisle, n)) |> 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() + 
  labs(title = "Number of items ordered in each aisle")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart |> 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) |>
  group_by(aisle) |> 
  count(product_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  knitr::kable()
```


Finally is a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week. This table has been formatted in an untidy manner for human readers. Pink Lady Apples are generally purchased slightly earlier in the day than Coffee Ice Cream, with the exception of day 5.

Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r}
instacart |>
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) |>
  group_by(product_name, order_dow) |>
  summarize(mean_hour = mean(order_hour_of_day)) |>
  pivot_wider(
    names_from = order_dow, 
    values_from = mean_hour) |>
  knitr::kable(digits = 2)
```

## Problem 2

```{r}
library(p8105.datasets)
data("brfss_smart2010")
brfss_smart2010
```

```{r}
brfss_smart = 
  brfss_smart2010 |> 
  as_tibble()
brfss_smart = 
  brfss_smart |>
  janitor::clean_names() |>
  rename(state = locationabbr, location_state = locationdesc) |>
  filter(topic %in% "Overall Health") |>
  mutate(response = fct_relevel(response, "Poor","Excellent"))

```

```{r}
brfss_smart |>
  filter(year == "2002") |>
  group_by(state) |>                                                    
  summarize(n = n_distinct(location_state)) |>  
  filter(n >= 7)
```

In 2002, CT, FL, MA, NC, Nj, PA were observed at 7 or more locations.

```{r}
brfss_smart |>
  filter(year == "2010") |>
  group_by(state) |>                                                    
  summarize(n = n_distinct(location_state)) |>  
  filter(n >= 7)
```

In 2010, CA, CO, FL, MA, MD, NC, NE, NJ, HY, OH, PA, SC, TX, WA were observed at 7 or more locations.

```{r}
brfss_smart |>
  filter(response=="Excellent")|>
  select(year, state, data_value)|>
  group_by(year, state)|>
  summarise(average_data_value = mean(data_value))|>
  ggplot(aes(x = year, y = average_data_value, color = state, group = state)) +
  geom_line()+
  labs(
    x = "Year",
    y = "Average Data Value",
    title = "Average Value Over Time Within a State"
  )
  
```


```{r}
brfss_smart |>
  group_by(year,response,state,data_value) |>
  filter(year %in% c("2006","2010")) |>
  filter(state %in% "NY")|>
  ggplot(aes(x = response, y = data_value)) + 
  geom_boxplot() + 
  facet_grid(. ~ year)
```


## Problem3

```{r}
nhanes_covar = 
  read_csv("nhanes_covar.csv",skip = 4) |>
  janitor::clean_names() |>
  filter(age > 21) |>
  mutate(
    sex = recode(sex, "1" = "male", "2" = "female"),
      education = recode(
      education, 
      "1" = "Less than high shcool", 
      "2" = "High school equivalent",
      "3" = "More than high school"),
  )|>
 mutate(
   sex = as.factor(sex), 
   education = as.factor(education)
 )|>
  na.omit() 
nhanes_covar
```
```{r}
nhanes_accel = 
  read_csv("nhanes_accel.csv") |>
  janitor::clean_names()|>
   pivot_longer(                                           
    min1:min1440,
    names_to = "number",
    values_to = "counts",
    names_prefix = "min"
  )
nhanes_accel
```

```{r}
nhanes_df = left_join(nhanes_covar,nhanes_accel,by = "seqn")
```


```{r}
education_table=select(nhanes_covar, sex | education)  
table(education_table)
```


At the High school equivalent education level, the number of male is 34 and the number of female is 23, more male than female. At less than high school education level,the number of male is 28 and the number of female is 27, more male than female. At more than high school education level,the number of male is 59 and the number of female is 54, more male than female.

```{r}
nhanes_covar |>
ggplot(aes(x = age, fill = sex )) +
  geom_density(alpha = .5) +
  facet_grid(. ~ education)
```

Based on the graphs, at the high school equivalent education level, the number of females exceeds the number of males as age increases. At the less than high school education level, the number of females first exceeds the number of males then becomes lower than that of males. At the more than high school education level, the number of females is originally higher than the number of males and then becomes lower than that of males. 


```{r}
accel_clean = 
  nhanes_df |>                                                                  
  group_by(seqn, sex, age, education) |>                        
  summarize(
    total_activity = sum(counts)                                
  )
accel_clean|>
ggplot(aes(x = age, y = total_activity, color = sex)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ education)+
  labs(
    title = "total activities against age",
    x = "age",
    y = "total activities",
  ) 
```
At high school equivalent and more than high school education level, overall females activity is higher than males. At less than high school education level, the overall males activity is higher than females. No matter education level and gender, total activity decreases as the age increases.

```{r}
nhanes_df |>
ggplot(aes(x = number, y = counts, group = seqn, color = sex)) +
  geom_line(alpha = .2) +
  facet_grid(. ~ education) +
  geom_smooth(aes(group = sex), se = FALSE)+
  labs(
    title = "total activities over 24-hour",
    x = "time(mins)",
    y = "total activities",
  ) 
```
Based on the plot, the 24-hour activity time courses for high school equivalent and less than high school education levels are similar. At more than high school education level, there are two peaks of activities. In addition, females have higher activities than males do.
