---
title: "p8105_hw3_zj2379"
author: "Zheshu Jiang"
date: "2023-10-12"
output: github_document
---

## Problem1
```{r}
library(p8105.datasets)
data("instacart")
library(tidyverse)
```

```{r}
instacart |> 
  count(aisle) |> 
  arrange(desc(n))
```

There are 134 aisles, with fresh vegetables and fresh fruits holding the most items ordered.

Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
instacart |> 
  count(aisle) |> 
  filter(n > 10000) |> 
  mutate(aisle = fct_reorder(aisle, n)) |> 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() + 
  labs(title = "Number of items ordered in each aisle")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart |> 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) |>
  group_by(aisle) |> 
  count(product_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  knitr::kable()
```


Finally is a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week. This table has been formatted in an untidy manner for human readers. Pink Lady Apples are generally purchased slightly earlier in the day than Coffee Ice Cream, with the exception of day 5.

Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r}
instacart |>
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) |>
  group_by(product_name, order_dow) |>
  summarize(mean_hour = mean(order_hour_of_day)) |>
  pivot_wider(
    names_from = order_dow, 
    values_from = mean_hour) |>
  knitr::kable(digits = 2)
```

## Problem 2

```{r}
library(p8105.datasets)
data("brfss_smart2010")
brfss_smart2010
```

```{r}
brfss_smart = 
  brfss_smart2010 |> 
  as_tibble()
brfss_smart = 
  brfss_smart |>
  janitor::clean_names() |>
  rename(state = locationabbr, location_state = locationdesc) |>
  filter(topic %in% "Overall Health") |>
  mutate(response = fct_relevel(response, "Poor","Excellent")) |>view()
```

```{r}
brfss_smart |>
  group_by(year,state) |>
  filter(year == "2002") |>
  count(state) |>
  filter(n >= 7)|>
  pivot_wider(
    names_from = state, 
    values_from = n)|>
  knitr::kable()
```

In 2002, AZ, CO, CT, DE, FL, GA ,HI, ID, IL, IN, KS, LA, MA, MD, ME, MI, MN, MO, NC, NE, NH, NJ, NV, NY, OH, OK, OR, PA, RI, SC, SD, TN, TX, UT, VT, WA were observed at 7 or more locations.

```{r}
brfss_smart |>
  group_by(year,state) |>
  filter(year == "2010") |>
  count(state) |>
  filter(n >= 7)|>
  pivot_wider(
    names_from = state, 
    values_from = n)|>
  knitr::kable()
```

In 2010, AL, AR, AZ, CA, CO, CT, DE, FL, GA, HI, IA, ID, IL, IN, KS, LA, MA, MD, ME, MI, MN, MO, MS, MT, NC, ND, NE, NH, NJ, NM, NV, NY, OH, OK, OR, PA, RI, SC, SD, TN, TX, UT, VT, WA, WY were observed at 7 or more locations.

```{r}
brfss_smart |>
  filter(response=="Excellent")|>
  select(year, state, data_value)|>
  group_by(year, state)|>
  summarise(average_data_value = mean(data_value))|>
  ggplot(aes(x = year, y = average_data_value, color = state, group = state)) +
  geom_line()+
  labs(
    x = "Year",
    y = "Average Data Value",
    title = "Average Value Over Time Within a State"
  )
  
```


Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
```{r}
brfss_smart |>
  group_by(year,response,state,data_value) |>
  filter(year %in% c("2006","2010")) |>
  filter(state %in% "NY")|>
  ggplot(aes(x = response, y = data_value)) + 
  geom_boxplot() + 
  facet_grid(. ~ year)
```


## Problem3



